\chapter*{Preface}
\section*{Welcome to the CN Reader}
This reader was inspired by the wonderfully crafted Languages \& Machines reader - a course you will all take during your second year as a Computing Science student (at the time of writing this).

What follows is the \textbf{first edition} of this reader, so please be patient with us if we have made any mistakes and/or omissions.

The first edition was developed by Boyan Karakostov and Mihai David in 2025.

\begin{warningblock}
This reader should not be considered a replacement for lecture slides and tutorials. We strongly encourage you to attend all sessions provided by the course.
\end{warningblock}

\section*{How to Use This Reader}
This reader is designed to be a companion to the course, providing additional explanations, examples, and exercises. It is structured to follow the course syllabus, with each section corresponding to a topic covered in lectures.

Sections marked with a \textbf{star} ($\star$) indicate optional content that is not essential for passing the course but provides deeper understanding of the topic at hand.

\section*{Prerequisites}
This reader assumes basic familiarity with C programming and various computer science concepts. If you are new to C or need a refresher, consider reviewing introductory materials on C programming.

\section*{Feedback}
We welcome your feedback on this reader. If you find any errors, have suggestions for improvements, or would like to see additional topics covered, please reach out to the professor of this course or visit the reader's \href{https://github.com/Code-For-Groningen/CN-Reader}{GitHub repository}\footnote{For the paper readers: github.com/Code-For-Groningen/CN-Reader}.

\section*{License and Usage}
This reader is licensed under the \href{https://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License}. You are free to share and adapt the material for non-commercial purposes, provided you give appropriate credit, indicate if changes were made, and distribute your contributions under the same license.

The code exerpts are licensed under GNU General Public License v3.0.

\section*{Updates and Errata}
This reader is a living document. We will periodically update it to correct errors, add new content, and improve clarity. Please check the \href{https://github.com/Code-For-Groningen/CN-Reader}{GitHub repository} for the latest version and any errata. The PDF provided by the course is a snapshot of the reader at the time of publication, and may not include the latest changes (but it will always be the most stable version).

If you'd like to report an error or suggest an improvement, please open an issue or submit a pull request on the GitHub repository. We appreciate your contributions to making this reader better for everyone. 

Pull request contributions will automatically be listed in the \hyperref[sec:contributions]{contributions section}.


\section*{Suggested Reading}
While this reader will cover the essential topics, we recommend the following books:
\begin{itemize}
    \item \textit{Computer Networking: A Top-Down Approach} by James K
    \item \textit{Beej's Guide to Network Programming} by Brian Hall - \href{https://beej.us/guide/bgnet/}{link}
\end{itemize}
